### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
Figures and text added to the architectural descriptions.

The \emph{uses structure} shows how elements are related with regard
to usage. One perspective of the uses structure is that the
elements in the figure are ''Overview创, ''Basket创 and ''Data创
which are all related and the database which is only related
to ''Data创. This shows that the overview page and the basket
has been decoupled from the database which therefore can be
replaced without affecting them.

@@

\fixme{Answer question 2.2}

>>>>

The \emph{uses structure} shows how elements are related with regard
to usage. One perspective of the uses structure is that the
elements in the figure are ``Overview'', ``Basket'' and ``Data''
which are all related and the database which is only related
to ``Data''. This shows that the overview page and the basket
has been decoupled from the database which therefore can be
replaced without affecting them.

@@

Selecting the relevant views shall actually be performed on
the basis of the architectural drivers which have not been
determined for the Beer Web Store. There are however several
models that provide a number of views that are often useful,
e.g. the ``4+1'' model \cite{kruchten1995} and the ``3+1''
model \cite{christensen2004archdesc} and many others.

As described in section \ref{sec:arch_desc_q1} the figure shows
parts of a module viewpoint (uses, layered), component \&
connector viewpoint (client-server) and an allocation viewpoint
(deployment) which are the recommended viewpoints in
\cite{christensen2004archdesc}.

These viewpoints are all relevant to the Beer Web Store example.
The Module viewpoint describes the internals of the webserver and how
the functionality is decomposed into units. The Component \& connector
viewpoint describes the runtime relations between the units and the
Allocation viewpoint describes the environment of the running
system.

In the following sections we will give examples on views for each
of the three viewpoints.

\subsubsection{Module Viewpoint}

Figure \ref{fig:ad_package} shows a package diagram of the Beer Web
Store and a decomposition of the web package. The Web package
contains the elements used for the web interface, 
the Overview page, the basket and the domain model. The domain model
depends on a Database package that contains the database facade and the
database facade uses some database package library, e.g. MySQL.

\begin{figure}[!htb]
\centerline{\epsfig{figure=figures/ad_package,scale=0.8 }}
\caption{Package diagram for the Beer Web Store}
\label{fig:ad_package}
\end{figure}

\subsubsection{Component \& Connector Viewpoint}

There are only two active components in the Beer Web Store, a web server,
e.g. Apache, and a database server. An active objects diagram will
not be included here.

Figure \ref{fig:ad_sequence} shows a sequence diagram where a user searches
for a an item ``tuborg'' and adds one of the search results to his basket.

\begin{figure}[!htb]
\centerline{\epsfig{figure=figures/ad_sequence,scale=0.6 }}
\caption{Sequence diagram showing a search and adding of an item}
\label{fig:ad_sequence}
\end{figure}

The domain model accesses the database through the database facade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment should
also be made.

\subsubsection{Allocation Viewpoint}

Figure \ref{fig:ad_allocation} shows a deployment view of the Beer
Web Store where the web server and the database is located on two
different servers. Clients can connect to the Beer Web Server
using a http web browser. The web server and database server
are connected through a local area network.

\begin{figure}[!htb]
\centerline{\epsfig{figure=figures/ad_allocation,scale=0.6 }}
\caption{Deployment view of the Beer Web Store}
\label{fig:ad_allocation}
\end{figure}

\fixme{Skal vi tilføje applikationen til Web serveren? Den indeholder
ikke nogen aktive komponenter.}
